\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2021-12-15 sections/methods.tex
Add: DC and TA step tables

  \subsection*{Sequence Processing (SP)}
  This module deals with processing the raw multiplexed 16S sequence data into demultiplexed, quality-controlled, trimmed sequences.
  It consists of the following processes: demulitplexing and trimming (includes quality control and filtering).
  The trimming process handles the quality control steps such as trimming adapters and trimming low-quality nucleotide stretches from the sequences.
  The parameters and tools in this process are fixed and are not available for user customization.
  The various tools used for the processes were adapted from \ac{qiime2} v2021.8.0~\cite{bolyenReproducibleInteractiveScalable2019}.

@@

  \subsection*{Taxonomy Assignment (TA)}
  \vspace{-5mm}
  This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or directly to the \ac{esv}s.
  In order to assign taxonomies to a particular sequence we need a taxonomy database and a query tool.
  The taxonomy database contains the collection of 16S sequences of micro-organisms of interest and the query tool allows one to compare a sequence of interest to all the sequences in the database to identify the best matches.
  Finally, a consensus method is used to identify the most probable match from the list of best matches.
  The pipeline incorporates \ac{gg} 13\_8~\cite{DeSantis2006}, SILVA 132~\cite{Quast2012} and the \ac{ncbi} (16S RefSeq as of Oct 2019)~\cite{Sayers2009} databases for taxonomy assignment and the Naive Bayes classifier from \ac{qiime2} and \ac{ncbi} blast as the query tools (from \ac{qiime2}).
  The consensus algorithm used is the default method used by the classifiers in \ac{qiime2}.

>>>>

  \subsection*{Sequence Processing (SP)}
  This module deals with processing the raw multiplexed 16S sequence data into demultiplexed, quality-controlled, trimmed sequences.
  It consists of the following processes: demultiplexing and trimming (includes quality control and filtering).
  The trimming process handles the quality control steps such as trimming adapters and trimming low-quality nucleotide stretches from the sequences.
  The parameters and tools in this process are fixed and are not available for user customization.
  The various tools used for the processes were adapted from \ac{qiime2} v2021.8.0~\cite{bolyenReproducibleInteractiveScalable2019}.

@@

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Module} & \textbf{Tool} & \textbf{References} \\
      \hline
      Denoising and Clustering & Closed reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
      Denoising and Clustering & Open reference & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
      Denoising and Clustering & De novo & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
      Denoising and Clustering & Dada2 & \cite{Callahan2016} \\
      Denoising and Clustering & Deblur & \cite{Amir2017,bolyenReproducibleInteractiveScalable2019} \\
      \hline
      Chimera checking & Uchime & \cite{rognesVSEARCHVersatileOpen2016,bolyenReproducibleInteractiveScalable2019} \\
      Chimera checking & Remove bimera & \cite{Callahan2016} \\
    \end{tabular}
    \caption{Tools used in the DC module}
    \label{tab:dc_tools}
  \end{table}

  \subsection*{Taxonomy Assignment (TA)}
  \vspace{-5mm}
  This module deals with assigning taxonomies to either the representative sequences of the \ac{otu}s or directly to the \ac{esv}s.
  In order to assign taxonomies to a particular sequence we need a taxonomy database and a query tool.
  The taxonomy database contains the collection of 16S sequences of micro-organisms of interest and the query tool allows one to compare a sequence of interest to all the sequences in the database to identify the best matches.
  Finally, a consensus method is used to identify the most probable match from the list of best matches.
  The pipeline incorporates \ac{gg} 13\_8~\cite{DeSantis2006}, SILVA 138~\cite{Quast2012} and the \ac{ncbi} (16S RefSeq as of Oct 2021)~\cite{Sayers2009} databases for taxonomy assignment.
  These databases were downloaded and built using the RESCRIPt qiime2 plugin~\cite{iiRESCRIPtReproducibleSequence2021}.
  The Naive Bayes classifier from \ac{qiime2} and \ac{ncbi} blast as the query tools (from \ac{qiime2}).
  The consensus algorithm used is the default method used by the classifiers in \ac{qiime2}.

  \begin{table}[h]
    \centering
    \small
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Module} & \textbf{Tool/Database} & \textbf{References} \\
      \hline
      Query tool & Blast & \cite{camachoBLASTArchitectureApplications2009} \\
      Query tool & Naive bayes classifier & \cite{bokulichOptimizingTaxonomicClassification2018} \\
      \hline
      Database & Greengenes & \cite{DeSantis2006} \\
      Database & SILVA & \cite{Quast2012} \\
      Database & NCBI RefSeq & \cite{Sayers2009} \\
    \end{tabular}
    \caption{Tools used in the TA module}
    \label{tab:ta_tools}
  \end{table}
